This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-28 article.tex
Fixed another typo

Fortunately, most common PDF readers don't seem to care how many
trailing bytes there are, at least when the PDF is version~1.4.
Unfortunately, some readers such as Adobe's try to be ``helpful,''
silently ``fixing'' the problem and offering to save the fixed version
upon exit.  We can at least partially fix the PDF, ensuring that
the \texttt{\%\%EOF} is exactly 20 bytes of the end of the file, by
creating a second uncompressed git object as the very end of the
packfile (right before the final 20~byte SHA-1 checksum).  We could
then move the trailer from the end of the original PDF at the start of
the pack to the new git object at the end of the pack.  Finally, we
could encapsulate the ``middle'' objects of the packfile inside a PDF
stream object, such that they are ignored by the PDF.  The tricky part
is that we would have to know how many bytes will be in that
stream \emph{before} we add the PDF to the git database.  That's
theoretically possible to do \textit{a priori}, but it'd be very labor
intensive to pull off.  Furthermore, using this approach will
completely break the inner PDF that is produced by cloning the
repository, since its trailer will then be in a separate file.
Therefore, I chose to live with Adobe's helpfulness and not pursue
this fix for the PoC.

>>>>

Fortunately, most common PDF readers don't seem to care how many
trailing bytes there are, at least when the PDF is version~1.4.
Unfortunately, some readers such as Adobe's try to be ``helpful,''
silently ``fixing'' the problem and offering to save the fixed version
upon exit.  We can at least partially fix the PDF, ensuring that
the \texttt{\%\%EOF} is exactly 20~bytes from the end of the file, by
creating a second uncompressed git object as the very end of the
packfile (right before the final 20~byte SHA-1 checksum).  We could
then move the trailer from the end of the original PDF at the start of
the pack to the new git object at the end of the pack.  Finally, we
could encapsulate the ``middle'' objects of the packfile inside a PDF
stream object, such that they are ignored by the PDF.  The tricky part
is that we would have to know how many bytes will be in that
stream \emph{before} we add the PDF to the git database.  That's
theoretically possible to do \textit{a priori}, but it'd be very labor
intensive to pull off.  Furthermore, using this approach will
completely break the inner PDF that is produced by cloning the
repository, since its trailer will then be in a separate file.
Therefore, I chose to live with Adobe's helpfulness and not pursue
this fix for the PoC.
